Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-20 Draft.Rmd
edited code 2

```{r Boost}
# Preprocessing "recipe"
preprocessing_recipe <- 
  recipes::recipe(value~lon+lat, data = training(dat_split)) %>%
  # convert categorical variables to factors
  recipes::step_string2factor(all_nominal()) %>%
  # combine low frequency factor levels
  recipes::step_other(all_nominal(), threshold = 0.01) %>%
  # remove no variance predictors which provide no predictive information 
  recipes::step_nzv(all_nominal()) %>%
  prep()

@@

# Find hyper parameter values which performed best at minimizing RMSE
xgboost_tuned %>%
  tune::show_best(metric = "rmse") %>%
  knitr::kable()
# Isolate the best performing hyperparameter values.
xgboost_best_params <- xgboost_tuned %>%
  tune::select_best("rmse")
knitr::kable(xgboost_best_params)

@@

train_prediction <- xgboost_model_final %>%
# fit the model on all the training data
  fit(formula = value ~ lon+lat, data = train_processed) %>%
  # predict the sale prices for the training data
  predict(new_data = train_processed) %>%
  bind_cols(training(ames_split))

xgboost_score_train <- train_prediction %>%
  yardstick::metrics(sale_price, .pred) %>%
  mutate(.estimate = format(round(.estimate, 2), big.mark = ","))

knitr::kable(xgboost_score_train)
```

>>>>

```{r Boost}
# Preprocessing "recipe"
preprocessing_recipe <- 
  recipes::recipe(value~lon+lat, data = training(dat_split)) %>%
  # Convert categorical variables to factors
  recipes::step_string2factor(all_nominal()) %>%
  # Combine low frequency factor levels
  recipes::step_other(all_nominal(), threshold = 0.01) %>%
  # Remove no variance predictors which provide no predictive information 
  recipes::step_nzv(all_nominal()) %>%
  prep()

@@

# Find hyper parameter values which performed best at minimizing RMSE
xgboost_tuned %>% tune::show_best(metric = "rmse") %>%knitr::kable()
# Isolate the best performing hyperparameter values.
xgboost_best_params <- xgboost_tuned %>% tune::select_best("rmse")
knitr::kable(xgboost_best_params)

@@

train_prediction <- xgboost_model_final %>%
  # Fit the model on all the training data
  fit(formula = value ~ lon+lat, data = train_processed) %>%
  # Predict the sale prices for the training data
  predict(new_data = train_processed) %>%
  bind_cols(training(ames_split))

xgboost_score_train <- train_prediction %>%
  yardstick::metrics(sale_price, .pred) %>%
  mutate(.estimate = format(round(.estimate, 2), big.mark = ","))
knitr::kable(xgboost_score_train)
```
